---
title: "Homework Assignment 2"
author: "Antonio Gonzalez"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
---

# Fundamentals of Data Management - Module 2

## Step 1: Import the Data

First we load the `readxl` package, which lets R read Excel files.
Then we import Sheet 3 of our spreadsheet, which contains the 5 fake study participants.

```{r}
# Load the package that reads Excel files
library(readxl)

# Import the fake data from Sheet 3 of our Excel file
# Make sure Gonzalez_hw2.xlsx is in the same folder as this .Rmd file
data <- read_excel("Gonzalez_hw2.xlsx", sheet = "Fake_Data_5_Participants")

# Print the full dataset so we can confirm it loaded correctly
print(data)
```

---

## Step 2: Summary Statistics for Height and Weight

Here we calculate the mean, median, minimum, and maximum
for both height_cm and weight_kg.

```{r}
# HEIGHT (cm)
cat("=== Height (cm) Statistics ===\n")
cat("Mean:  ", mean(data$height_cm),   "\n")
cat("Median:", median(data$height_cm), "\n")
cat("Min:   ", min(data$height_cm),    "\n")
cat("Max:   ", max(data$height_cm),    "\n")

cat("\n")

# WEIGHT (kg)
cat("=== Weight (kg) Statistics ===\n")
cat("Mean:  ", mean(data$weight_kg),   "\n")
cat("Median:", median(data$weight_kg), "\n")
cat("Min:   ", min(data$weight_kg),    "\n")
cat("Max:   ", max(data$weight_kg),    "\n")
```

---

## Step 3: Print Rows 2 and 3

Here we print only rows 2 and 3 from the dataset.

```{r}
# Print rows 2 and 3 (all columns)
cat("=== Rows 2 and 3 ===\n")
print(data[2:3, ])
```
